---
title: "HW1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(leaflet)
```

### Q1. Leaflet Figure (6 points)

Find or create a spatial dataset and make a leaflet figure to display some aspect of the dataset. Please include the relevant data in your repo (this will be private so only the instructor can see).

Note: you may need to change the output type to HTML (line 3 of the .RMD file ) to render a leaflet figure. You are also welcome to submit a screenshot of your figure.

### Q2. Data Simulation

Simulate data from a two-sample t-test framework.

#### a. Statistical Model (4 points)

Write out the statistical model for a two-sample t-test. Include clear notation for all model parameters.

Note that latex can be incorporated in .RMD documents

$$y \sim N()$$

#### b. Statistical Model (4 points)

Fit the model using `t.test()` and interpret the results.

#### c. Statistical Model (4 points)

Fit the model using `lm()` and/or `stan_glm()` and interpret the results.

### Q3. Data Analysis 

Using a dataset with butterfly movements, build a statistical model to predict butterfly "step distance". Additional details on the dataset are available: [https://data.mendeley.com/datasets/kpcgkfmpv8/1/files/abd61d7d-1188-4d1d-b669-59acc5f1f43c](https://data.mendeley.com/datasets/kpcgkfmpv8/1/files/abd61d7d-1188-4d1d-b669-59acc5f1f43c)

The code below creates a subset of butterfly movement distances for butterflies in flight. 

```{r, message = F}
butterfly <- read_csv('https://raw.githubusercontent.com/STAT505/project2/master/butterfly.csv') %>% filter(Behaviour == 'F', !is.na(Sex)) %>% select(-Behaviour, -Track.num)
```

#### a. Exploratory Data Visualization (4 points)

Create at least one figure, preferably more, to display the relationship between Step_distance and Species, Sex, (and/or) Air Temp.

Include informative captions, titles, and legends on your figure.


#### b. Model specification (4 points)

The goal is to build the best predictive model for step distance as a function of Species, Sex, and Air Temperature. Fit a few models and write out the "best" model that you can find.

If you opt to use a Bayesian approach, make sure to clearly state what priors you have used.

#### c. Model summary (4 points)

Summarize your model findings. Avoid only using technical statistical lingo and discuss the results in the context of butterflies.





